Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-28 paper/motivation.tex
small updates to motivation

Consider the backbone network in Figure~\ref{fig:example1}. It has three neighbors, a customer $Cust$ , a peer $Peer$, and a provider $Prov$. The policy of this network is shown on the right. It prefers the neighbors in a certain order ($P1$) and does not want to act as a transit between Peer and Prov ($P2$). It prefers to exchange traffic with Cust over $R1$ rather than $R2$ because $R1$ is cheaper ($P3$). To guard against another AS "hijacking" prefixes owned by Cust, it only sends traffic to them if Cust is on the AS path ($P4$). Finally, to guard against Cust accidentally becoming a transit for Prov, it does not use Cust for traffic that will later traverse Prov ($P5$).

To correctly implement this policy, the operators must compute and assign local preferences such that preferences at Cust-facing interfaces $>$ Peer-facing interfaces $>$ Prov-facing interfaces. At the same time, the preference at $R2$'s Cust-facing interface should be lower than that at $R1$, but higher than that at Prov-facing interface. To fully realize $P2$, MEDs will have to be appropriately configured as well. To implement $P3$ and $P4$, the operators may assign communities that indicate where a certain routing announcement entered the network. Then, R4 must not announce to $Peer$ routes that have communities that correspond to the R2-prov link but must announce communities for the $R2$-Cust and $R1$-Cust links. Finally, to implement $P4$ and $P5$, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.

We can now see how devising correct configurations for real, larger networks can quickly become a nightmare. Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several geography-, neighbor- or prefix-based exceptions to the default behavior. For example, a large AS with many peers in different geographic locations, may be faced with complex challenges like keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

@@

However, this implementation does not have the right behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services were sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

To avoid this problem, the operator may decide to disallow "valleys" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}. If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce the \CD{PG} externally. This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.

Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone. \sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures (if that is possible; otherwise, it generates a compile-time error). For aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.

>>>>

Consider the backbone network in Figure~\ref{fig:example1}. It has
three neighbors, a customer \CD{Cust}, a peer \CD{Peer}, and a provider \CD{Prov}. The policy of this network is shown on the right. It prefers the neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2). It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3). To guard against another AS "hijacking" prefixes owned by \CD{Cust}, it only sends traffic to them if \CD{Cust} is on the AS path (P4). Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).

To implement P1 of the policy, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3 the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. % Implementing P2 properly will require MEDs to be
% appropriately configured. 
\todd{I commented out the sentence about MEDs for P2, because the next
  two sentences seem to be about P2 instead of P3 and P4, which it
  originally said.  Please check}  To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.

Clearly it is no simple task to properly configure even this
small example network manually; devising correct configurations for real networks can quickly become a nightmare. Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. For example, a large AS with many peers in different geographic locations may be faced with complex challenges like keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

@@

However, this implementation does not have the right behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

To avoid this problem, the operator may decide to disallow "valley" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}. If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce the \CD{PG} externally. This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.

Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone. \sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures (if that is possible; otherwise, it generates a compile-time error). For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
